Data Preparation

### 2019-01-09 Data Preparation.Rmd
Importing student transcripts

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```

# Variable Engineering
We create a dataframe from the Corpus:
```{r}

>>>>

### Course Manuals
To expand our topic modeling of course content, we would like to analyse the material in the course manuals. The `corpus_manuals` contains the pdfs of the course manuals for the year 2017-2018 (most recently, available).
```{r}
corpus_manuals <- Corpus(x             = DirSource("Manuals 2017-18"),
                 readerControl = list(reader = readPDF(control = list(text = "-layout"))))
```
## Student Data
The tibble `transcripts` contains the transcripts of a selection of `7` alumni students from the college[^2]. `transcripts` contains information on each course taken by each student such as the receives grade, the semester in which teh course was taken as well as the calendar year.
```{r transcripts}
transcripts <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1kj7tlfJAoN0F7IdoS3saT-2iC3nuDLwnDItNtCKoZ4k/edit#gid=936718979')
print(transcripts)
```

# Variable Engineering

##Course Manual 
We create a dataframe from the Corpus:
```{r}
